\chapter{Conclusion and Future Works}
In this thesis, we have proposed a privacy-preserving human tracking algorithm, which receives top-view IR images as input and outputs the relative count of an enter or exit event at the doorway. The nature of low-resolution IR cameras prevents privacy violation fundamentally. We proposed to use a simple and effective segmentation threshold for object segmentation, use both centroids and central points to represent a binary blob, track the blob by nearest neighbor matching and finally filter the tracking result with an alpha-beta filter. The algorithm is capable to track single human passing through the doorway but also multiple humans at a common walking speed. We have deployed the algorithm on an ESP32-WROVER microcontroller and developed a doorway event counter that can operate independently for 2.5 days given the Wi-Fi infrastructure. The counted events are accumulated to obtain an estimation of building occupancy, which can be used in pandemic social distance regulation, HVAC optimization, and elder people caring.

Switching to a better IR camera that supports a longer detection range, higher resolution, and higher frame rate can enhance the algorithm accuracy as well as detect enter and exit events at various speeds. But the deployment cost will increase. Within the same hardware budget, a more complicated segmentation strategy has the largest potential to improve the counting result. The heat reflected from the surrounding environment poses a challenge in object segmentation and this should be taken into consideration in the development.